\documentclass[10pt,a4paper]{article}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{url}

\author{Heinz Karsten Hiekmann}
\title{Interview}
\begin{document}
	\maketitle
	\clearpage
\section{Anathem}
	\begin{enumerate}
		\item Do your neighbors burn one another alive?
		\item Do your shamans/pastors/witch doctors walk around on stilts?
		\item When a child gets sick do you pray?
		\item Sacrifice to a painted stick?
		\item Blame it on an old lady?
		\item Do you fancy you will see your dead dogs and cats in some sort of afterlife?
		\item Has anyone you know ever been ritually mutilated because they were seen reading a book?
		\item Do you live in wigwams, tents or skyscrapers?
		\item Can you read?
		\item What do you mean by reading?
		\item How do you interpret things that you have read?
		\item Do you know burning people at stake?
		\item Do you have criminals?
		\item Do you recognize them by their looks?
		\item Are criminals branded?
		\item Are criminals tattooed?
		\item Are criminals locked up?
		\item Does a woman with shaved eyebrows say \enquote{You are a criminal} and ring a silver bell?
		\item Or is it a man in a wig who strikes a block of wood with a hammer?
		\item Are accused persons thrust through a doughnut-shaped magnet?
		\item Is a forked stick used, that twitches when it is brought near evil?
		\item Does an Emperor hand down the decision from his throne written in vermilion ink and sealed with black wax, or is it rather that the accused must walk barefoot across a griddle?
		\item Is there a moving picture praxis that know all, but their secrets may only be unlocked by a court of eunuchs each of whom has memorized part of a long number?
		\item Or perhaps a mob shows up and throws rocks at the suspect until he's dead?
		\item Would you consider theft being a crime?
		\item Would you consider assault being a crime?
		\item Would you consider extortion being a crime?
		\item Would you consider sedition being a crime?
		\item Would you consider heresy being a crime?
		\item Where do you the shamans/pastors/witch doctors come from? 
		\item Are they THwoback-turnes Mystatgogues? 
		\item Are they Bottle Shakers?
	\end{enumerate}
	
\clearpage
\section{Dan Dennett - Maybe you're an atheist!}
\begin{enumerate}
	\item Do you listen to Dan Dennett?
	\item Do you want to switch the topic, because you are scared of what you may learn?
	\item Have you read into what Atheism is about?
	\item Is Jesus the son of God?
	\item Is Jesus THE son of God?
	\item Do you believe that Jesus is the son of God?
	\item Do you believe that God intervenes in people's lives
	\item Do you believe that God is on our side? 
	\item Do you believe that God takes sides on a football game?
	\item Do you believe that God created all the species, great and small?
	\item Do you believe that God is a benign force?
	\item Do you believe that Star Wars is a fantasy?
	\item Do you believe in a force that governs the whole universe?
	\item Do you believe in a force protecting us?
	\item Do you believe that God is a concept?
	\item Is a concept of God a concept?
	\item Do you think that love is just a word?
	\item Do you think that \enquote{love} is just a word?
	\item Is \enquote{cheesburger} just a word?
	\item Do you believe that the concept of God exists?
	\item Do you believe that thousands concepts of God exist?
	\item Do you believe that there are better concepts helping people lead better lives?
	\item How do you tell wishful thinking from genuine believe?
	\item Are they easily distinguished?
	\item Do you know the anguish of facing awful facts?
	\item How does your believe or religion tell wishful thinking from genuine believe?
	\item The Pope prays for world peace every Easter. What goes on in his mind, that he has never been heard?
\end{enumerate}

\clearpage
\section{Richard Dawkins}
\begin{enumerate}
	\item Do you believe in a prophet going to heaven on a winged horse?
	\item Is a child of Catholic parents catholic?
	\item Does religion grow by birth rate or conversion?
\end{enumerate}

\end{document}